06-assessing_lime_explanations

### 2019-02-09 journals/05-applying_lime.Rmd
worked more on journals...

##### Plot of Bin Frequencies

Heike made a plot with the structure of the one below when we began with the default settings of `lime`. This one has been created from the lime explanations with 2 quantile bins. It includes all three of the chosen features for each case in the testing dataset. For both sets, the cutoff of 0.275 < ccf occurs the most frequently.

```{r fig.height = 10}
# Plot of fequency for each bin division for 2 quantile bins
hamby224_test_explain %>%
  filter(situation == "2 quantile") %>%
  ggplot(aes(x = feature_desc)) +
  geom_bar() +
  coord_flip() + 
  facet_grid(set ~ .)
```

@@

```{r}
# Join the sensativity outputs with the test data
hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
  full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, 
           set:land2, rfscore, samesource) %>%
    mutate(diff = rfscore - model_prediction,
         nbins = as.numeric(as.character(nbins)),
         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                            sprintf("%.0f quantile", nbins),
                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                   sprintf("%.0f equally spaced", nbins),
                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "samesource",
                                          sprintf("%.0f samesource tree", nbins),
                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "rfscore",
                                            sprintf("%.0f rfscore tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation"))))) %>%
           fct_relevel("2 quantile", "3 quantile", "4 quantile",
                       "5 quantile", "6 quantile", "2 equally spaced",
                       "3 equally spaced", "4 equally spaced",
                       "5 equally spaced", "6 equally spaced",
                       "2 samesource tree", "3 samesource tree",
                       "4 samesource tree", "5 samesource tree",
                       "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))
```

>>>>

@@

```{r}
# Join the sensativity outputs with the test data
hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
  full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, 
           set:land2, rfscore, samesource) %>%
    mutate(diff = rfscore - model_prediction,
         nbins = as.numeric(as.character(nbins)),
         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                            sprintf("%.0f quantile", nbins),
                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                   sprintf("%.0f equally spaced", nbins),
                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "samesource",
                                          sprintf("%.0f samesource tree", nbins),
                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "rfscore",
                                            sprintf("%.0f rfscore tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation"))))) %>%
           fct_relevel("2 quantile", "3 quantile", "4 quantile",
                       "5 quantile", "6 quantile", "2 equally spaced",
                       "3 equally spaced", "4 equally spaced",
                       "5 equally spaced", "6 equally spaced",
                       "2 samesource tree", "3 samesource tree",
                       "4 samesource tree", "5 samesource tree",
                       "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))

write.csv(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.csv",
          row.names = FALSE)
```

### 2019-02-09 journals/06-assessing_lime_explanations.Rmd
worked more on journals...

---
title: "06-assessing_lime_explanations"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE)
```

@@

@@

@@

```{r fig.height = 8, fig.width = 10}
hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

>>>>

---
title: "06-assessing_lime_explanations"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
                      cache = TRUE)
```

@@

hamby224_sensitivity_joined <- read.csv("../data/hamby224_sensitivity_joined.csv")

@@

# Visualization Ideas

Heike made a plot with the structure of the one below when we began with the default settings of `lime`. This one has been created from the lime explanations with 2 quantile bins. It includes all three of the chosen features for each case in the testing dataset. For both sets, the cutoff of 0.275 < ccf occurs the most frequently.

```{r fig.height = 10}
# Plot of fequency for each bin division for 2 quantile bins
hamby224_test_explain %>%
  filter(situation == "2 quantile") %>%
  ggplot(aes(x = feature_desc)) +
  geom_bar() +
  coord_flip() + 
  facet_grid(set ~ .)
```

@@

```{r fig.height = 8, fig.width = 10, eval = FALSE}
hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")
